19Q1

### 2019-03-28 19Q1.Rmd
start CN comparisons

auc_all_ccls <- bind_rows(auc_unmatched_wide, ccls_not_drugscreened)
auc_all_ccls$HasMutationData <- with(auc_all_ccls, ifelse(Broad_ID %in% maf_df$Broad_ID, 1, 0))
auc_all_ccls$HasCopyNumberData <- with(auc_all_ccls, ifelse(Broad_ID %in% cn_melt$Broad_ID, 1, 0))
auc_all_ccls$HasGeneExpressionData <- with(auc_all_ccls, ifelse(Broad_ID %in% ge_melt$Broad_ID, 1, 0))
auc_all_ccls$WasCRISPRScreened <- with(auc_all_ccls, ifelse(Broad_ID %in% crispr_meta$Broad_ID, 1, 0))
auc_all_ccls$InCCLE <- with(auc_all_ccls, ifelse(WasDrugScreened == 0, 0, InCCLE))
auc_all_ccls$InCTRP <- with(auc_all_ccls, ifelse(WasDrugScreened == 0, 0, InCTRP))
auc_all_ccls$InGDSC <- with(auc_all_ccls, ifelse(WasDrugScreened == 0, 0, InGDSC))
auc_all_ccls[, -c(1:4)] <- apply(auc_all_ccls[, -c(1:4)], MARGIN = 2, FUN = as.numeric)
auc_all_ccls <- subset(auc_all_ccls, !(WasDrugScreened == 0 & WasCRISPRScreened == 0 & HasMutationData == 0 & HasGeneExpressionData == 0 & HasCopyNumberData == 0))
# write.csv.gz(auc_all_ccls, file = "./data_munging/pozdeyev2016/merged_auc_v20190327.3.csv.gz", row.names = FALSE, na = "NA")
```

```{r}
# test <- as.data.frame(table(auc_all_ccls$Cell_line))
# test <- filter(auc_all_ccls, Cell_line %in% c("KMH2", "MS1", "TT"))[, 1:12]

length(unique(sapply(strsplit(as.character(colnames(auc_all_ccls)[13:length(colnames(auc_all_ccls))]), split = "_"), function(x) x[1])))
```

>>>>

auc_all_ccls <- bind_rows(auc_unmatched_wide, ccls_not_drugscreened)
auc_all_ccls$HasMutationData <- with(auc_all_ccls, ifelse(Broad_ID %in% maf_df$Broad_ID, 1, 0))
auc_all_ccls$HasCopyNumberData <- with(auc_all_ccls, ifelse(Broad_ID %in% cn_melt$Broad_ID, 1, 0))
auc_all_ccls$HasGeneExpressionData <- with(auc_all_ccls, ifelse(Broad_ID %in% ge_melt$Broad_ID, 1, 0))
auc_all_ccls$WasCRISPRScreened <- with(auc_all_ccls, ifelse(Broad_ID %in% crispr_meta$Broad_ID, 1, 0))
auc_all_ccls$InCCLE <- with(auc_all_ccls, ifelse(WasDrugScreened == 0, 0, InCCLE))
auc_all_ccls$InCTRP <- with(auc_all_ccls, ifelse(WasDrugScreened == 0, 0, InCTRP))
auc_all_ccls$InGDSC <- with(auc_all_ccls, ifelse(WasDrugScreened == 0, 0, InGDSC))
auc_all_ccls[, -c(1:4)] <- apply(auc_all_ccls[, -c(1:4)], MARGIN = 2, FUN = as.numeric)
auc_all_ccls <- subset(auc_all_ccls, !(WasDrugScreened == 0 & WasCRISPRScreened == 0 & HasMutationData == 0 & HasGeneExpressionData == 0 & HasCopyNumberData == 0))
# write.csv.gz(auc_all_ccls, file = "./data_munging/pozdeyev2016/merged_auc_v20190327.3.csv.gz", row.names = FALSE, na = "NA")

# test <- as.data.frame(table(auc_all_ccls$Cell_line))
# test <- filter(auc_all_ccls, Cell_line %in% c("KMH2", "MS1", "TT"))[, 1:12]

# length(unique(sapply(strsplit(as.character(colnames(auc_all_ccls)[13:length(colnames(auc_all_ccls))]), split = "_"), function(x) x[1])))
```

### Compar to TCGA

```{r}
cn_seg <- read.delim("./data_munging/19Q1/copy_number_20190328.csv.gz", sep = ",")
cn_seg <- merge(ccl_histologies, cn_seg, by = "Broad_ID", all.y = TRUE)
cn_seg_lung <- filter(cn_seg, Histology == "lung")
```
